### 2020-02-19 Common/chapters/literature_review.tex
Johan and Julien: minor

Traditionally, building a computer-aider cancer diagnosis or detection (CAD) system consisted in two different parts: "Lesion  detection  and  false-positive  reduction.  Lesion  detection  was  primarily  based  on  algorithms  specific  to  the  detection task, resulting in many candidate lesions. False-positive reduction was commonly based on traditional  machine  learning  methods  to  reduce  the  false  positive  rate. However,  even  with  these  complicated and sophisticated programs, the general performance of conventional CAD systems was not good, thus hampering their widespread usage in clinical practice"~\cite{41}.\\
Nowadays, these two steps tend to disappear thanks to deep learning algorithms, in particular the ones based on convolutional neural networks. In fact, the latter can be considered as single-step CADs. For this reason, CAD systems are currently a trending topic in deep learning.\\
There mainly exists two types of CAD systems based on convolutional neural networks. The first one is called CADe for "computer-aided detection". Its primary goal is "to increase the detection rate of diseases while reducing the false negative  rate  possibly  due  to  the  observers’  mistakes  or  fatigue"~\cite{41}. This group includes medical  image  analysis  tasks  such  as  segmentation,  identification,  localization  and  detection. The other type is CADx for "computer-aided diagnosis" which aims at extracting the characteristics lesions.\\
This chapter goes through the main articles about CADe systems based on convolutional neural networks for each body part used in sections \ref{ch:paper_reproduction} and \ref{ch:transfer_learning}, i.e. prostate, lung and brain. Furthermore, it exclusively focuses on articles that used the same datasets as wthe ones used in this work.

>>>>

Traditionally, building a computer-aided cancer diagnosis or detection (CAD) system consisted in two different parts: "Lesion  detection  and  false-positive  reduction.  Lesion  detection  was  primarily  based  on  algorithms  specific  to  the  detection task, resulting in many candidate lesions. False-positive reduction was commonly based on traditional  machine  learning  methods  to  reduce  the  false  positive  rate. However,  even  with  these  complicated and sophisticated programs, the general performance of conventional CAD systems was not good, thus hampering their widespread usage in clinical practice"~\cite{41}.\\
Nowadays, these two steps tend to disappear thanks to deep learning algorithms, in particular the ones based on convolutional neural networks. In fact, the latter can be considered as single-step CADs. For this reason, CAD systems are currently a trending topic in deep learning.\\
There mainly exists two types of CAD systems based on convolutional neural networks. The first one is called CADe for "computer-aided detection". Its primary goal is "to increase the detection rate of diseases while reducing the false negative  rate  possibly  due  to  the  observers’  mistakes  or  fatigue"~\cite{41}. This group includes medical  image  analysis  tasks  such  as  segmentation,  identification,  localization  and  detection. The other type is CADx for "computer-aided diagnosis" which aims at extracting the characteristics lesions.\\
This chapter goes through the main articles about CADe systems based on convolutional neural networks for each body part used in sections \ref{ch:paper_reproduction} and \ref{ch:transfer_learning}, i.e. prostate, lung and brain. Furthermore, it exclusively focuses on articles that used the same datasets as the ones used in this work.
